---
title: "Actigraph Reliability Comparison with GGIR"
author: "Kathryn Freeman"
date: '`r Sys.Date()`'
output:
  html_notebook:
    toc: yes
    toc_float: true
    number_sections: no
    theme: cerulean
    code_folding: hide
---

## Coefficient of Agreement: Intraclass correlation Coefficient

* Interpreting ICC according to Koo and Li (2016)
  + Values less than 0.5 = poor reliability 
  + Values between 0.5 and 0.75 = moderate reliability
  + Values between 0.75 and 0.9 = good reliability
  + Values greater than 0.9 = excellent reliability



## Set-up {.tabset}

### Load packages
```{r}
library(here)
library(readr)
library(lubridate)
library(tidyverse) # ggplot, dplyr, tidyr, readr, purr, tibble
library(ICC) # ICC and CI
```

### Load data
```{r}
#Import data
df <- read_csv(here("data", "compiledsleepdata.csv"))

#View data
df

```

### ICC Functions
```{r}
ga2_md <- function(p, m, n, o, t, f, e){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a) 
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a) %>% round(digits = 4),
    "2.5% CI" = (icc_calc_ci$lcb) %>% round(digits = 4),
    "97.5% CI" = (icc_calc_ci$ucb) %>% round(digits = 4),
    "p-value" = (icc_calc_pval$pval) %>% round(digits = 4),
    "Nights" = (icc_calc$n) %>% round(digits = 1),
    "Raters" = (icc_calc$r) %>% round(digits = 1),
    "Class" = case_when(
    icc_calc$icc1a > 0.90 ~ "Excellent",
    icc_calc$icc1a <= 0.9 & icc_calc$icc1a > 0.75 ~ "Good",
    icc_calc$icc1a <= 0.75 & icc_calc$icc1a > 0.5 ~ "Moderate",
    icc_calc$icc1a < 0.5  ~ "Poor"))
    
print(classify_icc) 

plot <- ggplot((p), aes(g1, g2)) + geom_point() +
geom_smooth(method=lm, se=FALSE) +
labs(title = m, subtitle = t) +
labs(x = n) +
labs(y = o)


print(plot)
}


ga_md_ggir <- function(p, m, n, o, t, f, e){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a) 
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a) %>% round(digits = 4),
    "2.5% CI" = (icc_calc_ci$lcb) %>% round(digits = 4),
    "97.5% CI" = (icc_calc_ci$ucb) %>% round(digits = 4),
    "p-value" = (icc_calc_pval$pval) %>% round(digits = 4),
    "Nights" = (icc_calc$n) %>% round(digits = 1),
    "Raters" = (icc_calc$r) %>% round(digits = 1),
    "Class" = case_when(
    icc_calc$icc1a > 0.90 ~ "Excellent",
    icc_calc$icc1a <= 0.9 & icc_calc$icc1a > 0.75 ~ "Good",
    icc_calc$icc1a <= 0.75 & icc_calc$icc1a > 0.5 ~ "Moderate",
    icc_calc$icc1a < 0.5  ~ "Poor"))
    
print(classify_icc) 

plot <- ggplot((p), aes(ggir, markdown)) + geom_point() +
geom_smooth(method=lm, se=FALSE) +
labs(title = m, subtitle = t) +
labs(x = n) +
labs(y = o)


print(plot)
}


diary <- function(p){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a) 
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a) %>% round(digits = 4),
    "2.5% CI" = (icc_calc_ci$lcb) %>% round(digits = 4),
    "97.5% CI" = (icc_calc_ci$ucb) %>% round(digits = 4),
    "p-value" = (icc_calc_pval$pval) %>% round(digits = 4),
    "Nights" = (icc_calc$n) %>% round(digits = 1),
    "Raters" = (icc_calc$r) %>% round(digits = 1),
    "Class" = case_when(
    icc_calc$icc1a > 0.90 ~ "Excellent",
    icc_calc$icc1a <= 0.9 & icc_calc$icc1a > 0.75 ~ "Good",
    icc_calc$icc1a <= 0.75 & icc_calc$icc1a > 0.5 ~ "Moderate",
    icc_calc$icc1a < 0.5  ~ "Poor"))
    
print(classify_icc) 

}

mo2 <- function(p, m, n, o, t, f, e){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a) 
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a) %>% round(digits = 4),
    "2.5% CI" = (icc_calc_ci$lcb) %>% round(digits = 4),
    "97.5% CI" = (icc_calc_ci$ucb) %>% round(digits = 4),
    "p-value" = (icc_calc_pval$pval) %>% round(digits = 4),
    "Nights" = (icc_calc$n) %>% round(digits = 1),
    "Raters" = (icc_calc$r) %>% round(digits = 1),
    "Class" = case_when(
    icc_calc$icc1a > 0.90 ~ "Excellent",
    icc_calc$icc1a <= 0.9 & icc_calc$icc1a > 0.75 ~ "Good",
    icc_calc$icc1a <= 0.75 & icc_calc$icc1a > 0.5 ~ "Moderate",
    icc_calc$icc1a < 0.5  ~ "Poor"))
    
print(classify_icc) 

plot <- ggplot((p), aes(m1, m1)) + geom_point() +
geom_smooth(method=lm, se=FALSE) +
labs(title = m, subtitle = t) +
labs(x = n) +
labs(y = o)


print(plot)
}

ga_mo <- function(p, f, n, o, t){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a) 
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a) %>% round(digits = 4),
    "2.5% CI" = (icc_calc_ci$lcb) %>% round(digits = 4),
    "97.5% CI" = (icc_calc_ci$ucb) %>% round(digits = 4),
    "p-value" = (icc_calc_pval$pval) %>% round(digits = 4),
    "Nights" = (icc_calc$n) %>% round(digits = 1),
    "Raters" = (icc_calc$r) %>% round(digits = 1),
    "Class" = case_when(
    icc_calc$icc1a > 0.90 ~ "Excellent",
    icc_calc$icc1a <= 0.9 & icc_calc$icc1a > 0.75 ~ "Good",
    icc_calc$icc1a <= 0.75 & icc_calc$icc1a > 0.5 ~ "Moderate",
    icc_calc$icc1a < 0.5  ~ "Poor"))
    
print(classify_icc) 

plot <- ggplot((p), aes(g, m)) + geom_point() +
geom_smooth(method=lm, se=FALSE) +
labs(title = f, subtitle = t) +
labs(x = n) +
labs(y = o)


print(plot)
}
```

### Time Functions
```{r}
adjtime <- function(x) {df %>%
  mutate(rawtime = (((hour(hms(x)*60) + (minute(hms(x)) + (600)))))) %>%
  mutate(adjtime = (ifelse(rawtime>1439, rawtime-1440, rawtime)))
}

sleepduration <- function (y) {df %>%
  mutate(dur = (adjtime(df$etime)$adjtime - (adjtime(df$stime)$adjtime)))
}

sleepmid <- function (w) {df %>%
  mutate(mid = ((adjtime(df$etime)$adjtime + (adjtime(df$stime)$adjtime))/2))
}
```

## Two GENEActivs using Markdown data {.tabset}
#### Kate Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
ga2_md(((pivot_wider(df %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (tinb)))), "Time Spent in Bed", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using Markdown")
```
### Percent Sleep (pslp)
#### Percent Sleep (pslp)
##### pslp = (Sleep Minutes / Duration in Bed) x 100
```{r}

ga2_md(((pivot_wider(df %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (pslp)))), "Percent Sleep", 
  "GENEActiv 1 (percent)", "GENEActiv 2 (percent)", 
  "Two GENEActivs using Markdown")
```
### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (smin))), "Sleep Minutes", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using Markdown")
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (wmin))), "Wake Minutes", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using Markdown")
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
ga2_md((pivot_wider(adjtime(df$etime) %>% 
  filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Wake-up Time", 
  "GENEActiv 1 (mins after 2pm)",
       "GENEActiv 2 (mins after 2pm)", "Two GENEActivs using Markdown")
```

### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
ga2_md((pivot_wider(adjtime(df$stime) %>% 
  filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Sleep Time", "GENEActiv 1 (mins after 2pm)",
       "GENEActiv 2 (mins after 2pm)", "Two GENEActivs using Markdown")
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
ga2_md((pivot_wider(sleepduration(1) %>% 
  filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = dur)), "Sleep Duration", "GENEActiv 1 (mins)", 
       "GENEActiv 2 (mins)", "Two GENEActivs using Markdown")
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}

ga2_md((pivot_wider(sleepmid(1) %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = mid))
, "Sleep Midpoint", "GENEActiv 1 (mins after 2pm)",
       "GENEActiv 2 (mins after 2pm)", "Two GENEActivs using Markdown")
```









## Two GENEActivs using GGIR data {.tabset}
#### Kate & Steve Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (tinb))), "Time Spent in Bed", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using GGIR")
```
### Percent Sleep (pslp)
#### Percent Sleep (pslp)
##### pslp = (Sleep Minutes / Duration in Bed) x 100
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (pslp))), "Percent Sleep", 
  "GENEActiv 1 (percent)", "GENEActiv 2 (percent)", 
  "Two GENEActivs using GGIR")
```
### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (smin))), "Sleep Minutes", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using GGIR")
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}
ga2_md((pivot_wider(df %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (wmin))), "Wake Minutes", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using GGIR")
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
ga2_md((pivot_wider(adjtime(df$etime) %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Wake-up Time", 
  "GENEActiv 1 (mins after 2pm)","GENEActiv 2 (mins after 2pm)", 
  "Two GENEActivs using GGIR")
```
### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
ga2_md((pivot_wider(adjtime(df$stime) %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Sleep Time", 
  "GENEActiv 1 (mins after 2pm)", "GENEActiv 2 (mins after 2pm)", 
  "Two GENEActivs using GGIR")
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
ga2_md((pivot_wider(sleepduration(1) %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = dur)), "Sleep Duration", 
  "GENEActiv 1 (mins)", "GENEActiv 2 (mins)", "Two GENEActivs using GGIR")
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}
ga2_md((pivot_wider(sleepmid(1) %>% filter(analysis == "ggir") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = mid)), "Sleep Midpoint", 
  "GENEActiv 1 (mins after 2pm)", "GENEActiv 2 (mins after 2pm)", 
  "Two GENEActivs using GGIR")
```










## GENEActiv Markdown vs GENEActiv GGIR data {.tabset}
#### Kate Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g1") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (tinb))), "Time Spent in Bed", "GENEActiv 1 GGIR (mins)", 
           "GENEActiv 1 Markdown (mins)", "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g2") %>%
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (tinb))), "Time Spent in Bed", "GENEActiv 2 GGIR (mins)", 
           "GENEActiv 2 Markdown (mins)", "GENEActiv 2 GGIR vs Markdown")
```
### Percent Sleep (pslp)
#### Percent Sleep (pslp)
##### pslp = (Sleep Minutes / Duration in Bed) x 100
```{r}
ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g1") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (pslp))), "Percent Sleep", "GENEActiv 1 GGIR (percent)", 
           "GENEActiv 1 Markdown (percent)", "GENEActiv 1 GGIR vs Markdown")


ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g2") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (pslp))), "Percent Sleep", "GENEActiv 2 GGIR (percent)", 
           "GENEActiv 2 Markdown (percent)", "GENEActiv 2 GGIR vs Markdown")
```
### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g1") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (smin))), "Sleep Minutes", "GENEActiv 1 GGIR (mins)", 
           "GENEActiv 1 Markdown (mins)", "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g2") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (smin))), "Sleep Minutes", "GENEActiv 2 GGIR (mins)", 
           "GENEActiv 2 Markdown (mins)", "GENEActiv 2 GGIR vs Markdown")
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}
ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g1") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (wmin))), "Wake Minutes", "GENEActiv 1 GGIR (mins)", 
           "GENEActiv 1 Markdown (mins)", "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(df %>% filter(actigraph == "g2") %>% 
  filter(wearer == "Kate"), night, names_from = analysis, 
  values_from = (wmin))), "Wake Minutes", "GENEActiv 2 GGIR (mins)", 
           "GENEActiv 2 Markdown (mins)", "GENEActiv 2 GGIR vs Markdown")
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}

ga_md_ggir((pivot_wider(adjtime(df$etime) %>% 
  filter(actigraph == "g1") %>% filter(wearer == "Kate"), 
  night, names_from = analysis, values_from = (adjtime)))
, "Wake-up Time", 
           "GENEActiv 1 GGIR (mins after 2pm)",
           "GENEActiv 1 Markdown (mins after 2pm)", 
           "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(adjtime(df$etime) %>% 
  filter(actigraph == "g2") %>% filter(wearer == "Kate"), 
  night, names_from = analysis, values_from = (adjtime))), "Wake-up Time", 
           "GENEActiv 2 GGIR (mins after 2pm)",
           "GENEActiv 2 Markdown (mins after 2pm)", 
           "GENEActiv 2 GGIR vs Markdown")
```
### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
ga_md_ggir((pivot_wider(adjtime(df$stime) %>% 
 filter(actigraph == "g1") %>% 
 filter(wearer == "Kate"), 
 night, names_from = analysis, values_from = (adjtime))), "Sleep Time", 
           "GENEActiv 1 GGIR (mins after 2pm)",
           "GENEActiv 1 Markdown (mins after 2pm)", 
           "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(adjtime(df$stime) %>% 
 filter(actigraph == "g2") %>% 
 filter(wearer == "Kate"), 
 night, names_from = analysis, values_from = (adjtime))), "Sleep Time", 
           "GENEActiv 2 GGIR (mins after 2pm)",
           "GENEActiv 2 Markdown (mins after 2pm)", 
           "GENEActiv 2 GGIR vs Markdown")
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
ga_md_ggir((pivot_wider(sleepduration(1) %>% 
 filter(actigraph == "g1") %>%
 filter(wearer == "Kate"), 
 night, names_from = analysis, values_from = dur)), "Sleep Duration", 
           "GENEActiv 1 GGIR (mins)",
           "GENEActiv 1 Markdown (mins)", 
           "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(sleepduration(1) %>% 
  filter(actigraph == "g2") %>% 
  filter(wearer == "Kate"), 
  night, names_from = analysis, values_from = dur)), "Sleep Duration", 
           "GENEActiv 2 GGIR (mins)",
           "GENEActiv 2 Markdown (mins)", 
           "GENEActiv 2 GGIR vs Markdown")
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}
ga_md_ggir((pivot_wider(sleepmid(1) %>% 
 filter(actigraph == "g1") %>% 
 filter(wearer == "Kate"), 
 night, names_from = analysis, values_from = mid)), "Sleep Midpoint", 
           "GENEActiv 1 GGIR (mins after 2pm)",
           "GENEActiv 1 Markdown (mins after 2pm)", 
           "GENEActiv 1 GGIR vs Markdown")

ga_md_ggir((pivot_wider(sleepmid(1) %>% 
  filter(actigraph == "g2") %>% 
  filter(wearer == "Kate"), 
  night, names_from = analysis, values_from = mid)), "Sleep Midpoint", 
           "GENEActiv 2 GGIR (mins after 2pm)",
           "GENEActiv 2 Markdown (mins after 2pm)", 
           "GENEActiv 2 GGIR vs Markdown")
```







## GENEActiv GGIR data vs Diary + GENEActiv Markdown data vs Diary {.tabset}
#### Kate Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
diary((pivot_wider(df %>% 
  filter(test == "same") %>%
  filter(wearer == "Kate") %>%
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (tinb))))

diary((pivot_wider(df %>% 
  filter(test == "same") %>%                              
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (tinb)))
)
```

### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
diary((pivot_wider(df %>%
  filter(wearer == "Kate") %>%                                
  filter(test == "same") %>%                                
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (smin)))
)


diary((pivot_wider(df %>% 
  filter(test == "same") %>%                              
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (smin))))
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}

diary((pivot_wider(df %>%
  filter(wearer == "Kate") %>%
  filter(test == "same") %>%                                
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (wmin))))


diary((pivot_wider(df %>% 
  filter(test == "same") %>%                              
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (wmin)))
)
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
diary((pivot_wider(adjtime(df$etime) %>%
  filter(wearer == "Kate") %>%                                  
  filter(test == "same") %>%                                  
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))

diary((pivot_wider(adjtime(df$etime) %>%
  filter(test == "same") %>%                                
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))
```
### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
diary((pivot_wider(adjtime(df$stime) %>%
  filter(wearer == "Kate") %>%                                 
  filter(test == "same") %>%                                 
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))

diary((pivot_wider(adjtime(df$stime) %>%
  filter(wearer == "Kate") %>%                               
  filter(test == "same") %>%                               
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
diary((pivot_wider(sleepduration(1) %>%
  filter(wearer == "Kate") %>%                               
  filter(test == "same") %>%                               
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = dur)))

diary((pivot_wider(sleepduration(1) %>%
  filter(test == "same") %>%                             
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = dur)))
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}
diary((pivot_wider(sleepmid(1) %>%
  filter(wearer == "Kate") %>%                               
  filter(test == "same") %>%                               
  filter(analysis == "ggir" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = mid)))

diary((pivot_wider(sleepmid(1) %>%
  filter(test == "same") %>%                             
  filter(analysis == "markdown" | analysis == "diary") %>% 
  filter(actigraph == "g1" | actigraph == "g2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = mid)))
```






## Motionlogger Data & Motionlogger with Diary {.tabset}
#### Kate Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
mo2((pivot_wider(df %>%
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (tinb))),
  "Time Spent in Bed", "Motionlogger 1 (mins)", 
       "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(df %>% filter(test == "same") %>%  
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (tinb))))
```
### Percent Sleep (pslp)
#### Percent Sleep (pslp)
##### pslp = (Sleep Minutes / Duration in Bed) x 100
```{r}
mo2((pivot_wider(df %>%
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (pslp))), "Percent Sleep", "Motionlogger 1 (mins)", 
       "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(df %>% filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (pslp))))
```
### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
mo2((pivot_wider(df  %>% 
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (smin))), "Sleep Minutes", 
  "Motionlogger 1 (mins)", "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(df  %>% filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (smin))))
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}
mo2((pivot_wider(df %>% 
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (wmin))), 
  "Wake Minutes", "Motionlogger 1 (mins)", 
       "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(df %>% filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (wmin))))
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
mo2((pivot_wider(adjtime(df$etime) %>% 
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Wake-up Time", 
  "Motionlogger 1 (mins)", "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(adjtime(df$etime) %>% filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))
```
### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
mo2((pivot_wider(adjtime(df$stime) %>%  
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = (adjtime))), "Sleep Time", 
  "Motionlogger 1 (mins)", "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(adjtime(df$stime) %>%  filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = (adjtime))))
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
mo2((pivot_wider(sleepduration(1) %>%  
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = dur)), "Sleep Duration", 
  "Motionlogger 1 (mins)", "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(sleepduration(1) %>%  filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = dur)))
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}
mo2((pivot_wider(sleepmid(1) %>% 
  filter(actigraph == "m1" | actigraph == "m2"), night, 
  names_from = actigraph, values_from = mid)), "Sleep Midpoint", 
  "Motionlogger 1 (mins)", "Motionlogger 2 (mins)", "Two Motionloggers")

diary((pivot_wider(sleepmid(1) %>% filter(test == "same") %>%
  filter(actigraph == "m1" | actigraph == "m2" | actigraph == "d"), night, 
  names_from = actigraph, values_from = mid)))
```



## GENEActiv GGIR/Markdown vs Motionlogger data {.tabset}
#### Anna, Kate & Ross Wearing Devices

### Time in Bed (tinb)
#### Time in Bed (tinb)
##### tinb = total duration of time spent in bed
```{r}
ga_mo((pivot_wider(df %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (tinb))), "Time Spent in Bed", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(df %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (tinb))), "Time Spent in Bed", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Percent Sleep (pslp)
#### Percent Sleep (pslp)
##### pslp = (Sleep Minutes / Duration in Bed) x 100
```{r}
ga_mo((pivot_wider(df  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (pslp))), "Percent Sleep", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(df %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (pslp))), "Percent Sleep", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Sleep Minutes (smin)
#### Sleep Minutes (smin)
##### smin = minutes asleep in bed
```{r}
ga_mo((pivot_wider(df  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (smin))), "Sleep Minutes", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(df %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (smin))), "Sleep Minutes", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Wake Minutes (wmin)
#### Wake Minutes (wmin)
##### wmin = minutes awake in bed
```{r}
ga_mo((pivot_wider(df %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (wmin))), "Wake Minutes", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(df %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (wmin))), "Wake Minutes", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Wake-up Time (etime)
#### Wake-up Time (etime)
##### etime = time awakened from sleep in morning
###### Adjusted to 2pm = 0:00 in minutes since 2pm
```{r}
ga_mo((pivot_wider(adjtime(df$etime)  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (adjtime))), "Wake-up Time", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(adjtime(df$etime) %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (adjtime))), "Wake-up Time", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Sleep Time (stime)
#### Sleep Time (stime)
##### stime = time fell asleep at night
###### Adjusted to 2pm = 0:00 in mins since 2pm
```{r}
ga_mo((pivot_wider(adjtime(df$stime)  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (adjtime))), 
  "Sleep Time", "GENEActiv (mins)", 
  "Motionlogger (mins)", "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(adjtime(df$stime) %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (adjtime))), "Sleep Time", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```
### Total Sleep Duration (dur)
#### Total Sleep Duration (dur)
##### dur = time between fall asleep time and wake-up time
```{r}
ga_mo((pivot_wider(sleepduration(1)  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = dur)), "Sleep Duration", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(sleepduration(1) %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (dur))), "Sleep Duration", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")
```

### Sleep Midpoint (mid)
#### Sleep Midpoint (mid)
##### mid = middle of sleep period
```{r}
ga_mo((pivot_wider(sleepmid(1)  %>% 
  filter(analysis == "ggir" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = mid)), "Sleep Midpoint", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using GGIR vs Motionlogger")

ga_mo((pivot_wider(sleepmid(1) %>% 
  filter(analysis == "markdown" | analysis == "motionlogger") %>% 
  filter(actigraph == "g" | actigraph == "m"), night, 
  names_from = actigraph, values_from = (mid))), "Sleep Midpoint", 
  "GENEActiv (mins)", "Motionlogger (mins)", 
  "GENEActiv using Markdown vs Motionlogger")

```
