---
title: "Actigraph Reliability Comparison with GGIR"
author: "Kathryn Freeman"
date: '`r Sys.Date()`'
output:
  html_notebook:
    toc: yes
    toc_float: true
    number_sections: no
    theme: cerulean
    code_folding: hide
---

## Coefficient of Agreement: Intraclass correlation Coefficient

* Interpreting ICC
  + Values less than 0.5 = poor reliability 
  + Values between 0.5 and 0.75 = moderate reliability
  + Values between 0.75 and 0.9 = good reliability
  + Values greater than 0.9 = excellent reliability

A Guideline of Selecting and Reporting Intraclass Correlation Coefficients for Reliability Research, Koo 2016 

* ICC type
  + ICC(1) Each subject is assessed by a different set of randomly selected raters, and the
  reliability is calculated from a single measurement. Uncommonly used in clinical
  reliability studies.
  + ICC(1,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
  + ICC(2) Each subject is measured by each rater, and raters are considered representative
  of a larger population of similar raters. Reliability calculated from a single
  measurement.
  + ICC(2,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
  + ICC(3) Each subject is assessed by each rater, but the raters are the only raters of
  interest. Reliability calculated from a single measurement.
  + ICC(3,k) As above, but reliability is calculated by taking an average of the k raters’
  measurements.
    + Please note that subjects in this case are nights of sleep and raters are the two actigraphs
  
Model ICC(2) appears most applicable to the sleep data set

## Set-up {.tabset}

### Load packages
```{r}
library(here)
library(readr)
library(lubridate)
library(tidyverse) # ggplot, dplyr, tidyr, readr, purr, tibble
library(ICC) # ICC and CI
```

### Load data
```{r}
#Import data
df <- read_csv(here("data", "compiledsleepdata.csv"))

#View data
df


```


## GENEActiv Markdown data {.tabset}

### Time in Bed
```{r}
tinb_ga2_md <- (pivot_wider(df %>% filter(analysis == "markdown") %>% 
  filter(actigraph == "g1" | actigraph == "g2"), night, 
  names_from = actigraph, values_from = (tinb)))

ga2_md <- function(p){
  
  icc_calc <- irrICC::icc1a.fn(p) 
  icc_calc_ci <- irrICC::ci.ICC1a(p) 
  icc_calc_pval <- irrICC::pvals.ICC1a(p)

  "ICC" <- (icc_calc$icc1a)
  
classify_icc <- 
    c("ICC" = (icc_calc$icc1a),
    "2.5% CI" = (icc_calc_ci$lcb),
    "97.5% CI" = (icc_calc_ci$ucb),
    "p-value" = (icc_calc_pval$pval),
    "Night Number" = (icc_calc$n),
    "Rater Number" = (icc_calc$r),
    "Classification" = case_when(
    "ICC" > 0.74 ~ "Excellent",
    "ICC" <= 0.74 & ICC > 0.59 ~ "Good",
    "ICC" <= 0.59 & ICC > 0.40 ~ "Fair",
    "ICC" < 0.40  ~ "Poor"))
 
  print(classify_icc)

plot <- ggplot((p), aes(x=g1, y=g2)) + geom_point() +
geom_smooth(method=lm, se=FALSE) +
labs(title = "Time Spent in Bed", subtitle = "Two GENEActivs using Markdown") +
labs(x = "GENEActiv 1 (mins)") +
labs(y = "GENEActiv 2 (mins)")


print(plot)
}
```

```{r}
ga2_md(tinb_ga2_md)
```
```{r}
icc_calc <- irrICC::icc1a.fn(tinb_ga2_md) 
  icc_calc_ci <- irrICC::ci.ICC1a(tinb_ga2_md) 
  icc_calc_pval <- irrICC::pvals.ICC1a(tinb_ga2_md)

  "ICC" <- (icc_calc$icc1a)
  
classify_icc <- 
    c("p-value" = (icc_calc_pval$pval),
    "ICC" = (icc_calc$icc1a),
    "2.5% CI" = (icc_calc_ci$lcb),
    "97.5% CI" = (icc_calc_ci$ucb),
    "Night Number" = (icc_calc$n),
    "Rater Number" = (icc_calc$r),
    "Classification" = case_when(
    "ICC" > 0.74 ~ "Excellent",
    "ICC" <= 0.74 & ICC > 0.59 ~ "Good",
    "ICC" <= 0.59 & ICC > 0.40 ~ "Fair",
    "ICC" < 0.40  ~ "Poor"))

print(classify_icc)
```


```{r}
dur.df <- data %>% select(wearer, dur, actigraph, analysis) %>% 
  filter(actigraph == "g1" | actigraph == "g2") %>% 
  filter(analysis == "markdown") %>% 
  group_by(actigraph, wearer, analysis) 

irr::icc(dur.df, model = c("twoway"), type = c("agreement"), unit = c("single"))

dur.df

%>% group_by(actigraph, wearer, analysis) %>% select(dur)
group_by(actigraph) %>% group_split(dur, .keep = TRUE)
```

